---
title: "Initial Lyric Dataframe"
author: "Dave Gruenewald"
date: "February 26, 2018"
output: 
  html_document:
    toc: true
---

## Pick a song with rich lyrics

I've been digging some Pink Floyd lately, so let's try "Comfortably Numb".

```{r}
library(tidyverse)
# devtools::install_github("josiahparry/geniusR")
library(geniusR)

song <- "Nights in White Satin"

raw_df <- geniusR::genius_lyrics(artist = "Moody Blues",
                                 song = song,
                                 info = "all")
```

Looks like there are a few special characters, so I'll need to clean that up a little bit.  


## Remove special characters

```{r}
parsed_df <- raw_df %>% 
  # filter(!(text %in% c("Roger Waters", "David Gilmour"))) %>% 
  mutate(text = lyric %>% 
           str_to_lower() %>% 
           str_replace_all("[[:punct:]]", "") %>% 
           str_trim(),
         line = row_number(),
         line_length = str_length(text)) %>% 
  separate_rows(text, sep = " ") %>% 
  mutate(text_length = str_length(text),
         word = row_number())

```

There we go, I removed punctuation, all text is now lower case, and each word is its own line.  `r nrow(parsed_df)` words for "`r song`".  Now time to plot redundancies.

But first maybe look at ratio of total words vs. unique words

```{r}
rep_df <- parsed_df %>% 
  left_join(.,
            parsed_df %>% 
              group_by(text) %>% 
              tally(),
            by = "text")

parsed_df %>% 
  distinct(text)

# tmp <- diag(1, nrow(parsed_df) %>% 
#               rep(., 2))
# 
# colnames(tmp) <- parsed_df %>% pull(text)
# rownames(tmp) <- parsed_df %>% pull(text)
# 
# as_data_frame(tmp)
# 
# parsed_df %>% 
#   pull(text)
# 
# plot(tmp)

```

